Experiments and Modeling of the Autoignition of Methyl Pentanoate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-09-26 revision-1/revised-paper/methyl-valerate.tex
Finish Jackie's reviewer comments

This work provides additional data for the autoignition of MV. Data is collected in a RCM under
engine relevant conditions spanning from \SIrange{15}{30}{\bar}, equivalence ratios \((\phi)\) from
\numrange{0.25}{2.0}, and temperatures from \SIrange{680}{1050}{\K}. The NTC region of MV is mapped
out to provide additional information on the fidelity of using MV as a biodiesel surrogate and
insights into the autoignition chemistry of large methyl esters.

@@

\begin{center}
    \captionsetup{type=figure}
    \resizebox{\textwidth}{!}{\input{figures/simulation-comparison.pgf}}
    \caption{Comparison of experimental (\(\tau\) and \(\tau_1\)) and simulated (\(\tau\)) ignition
    delays computed using the procedure described in \cref{sec:experimental-modeling}. a)
    \SI{15}{\bar}, b) \SI{30}{\bar}.}
    \label{fig:simulation-comparison}
\end{center}

>>>>

This work provides additional data for the autoignition of MV. Data is collected in a RCM under
engine relevant conditions spanning from \SIrange{15}{30}{\bar}, equivalence ratios \((\phi)\) from
\numrange{0.25}{2.0}, and temperatures from \SIrange{680}{1050}{\K}. The NTC region of MV is mapped
out to provide additional information on the fidelity of using MV as a biodiesel surrogate and on
the autoignition chemistry of large methyl esters.

@@

\begin{center}
    \captionsetup{type=figure}
    \resizebox{\textwidth}{!}{\input{figures/simulation-comparison.pgf}}
    \caption{Comparison of experimental and simulated ignition delays computed using the procedure
    described in \cref{sec:experimental-modeling}. a) \SI{15}{\bar}, b) \SI{30}{\bar}.}
    \label{fig:simulation-comparison}
\end{center}
